Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-03-16 src/tex/ms.tex
Reword PSD paragraph

In order to recalibrate the model, we need to define an objective function that
quantify the performance of the model. A common choice for such metric is the
\textit{mismatch} function \citep{husa2016frequency}. It is defined as
\begin{align} \label{eq:mismatch}
	\mathcal{M}(h_1, h_2)=1-\max_{t_0, \phi_0}\langle \hat{h}_1, \hat{h}_2\rangle,
\end{align}
where $h_{1,2}$ are the two GW waveform we are comparing, and $t_0$ and $\phi_0$
are time shift and phase shift respectively. The $\langle h_1, h_2 \rangle$ is
commonly referred as the inner product, which is defined as 
\begin{align}\label{eq:inner_prod}
	\langle h_1, h_2 \rangle = 4\Re\int_{f_{\mathrm{min}}}^{f_{\mathrm{max}}}\frac{h_1(f)h_2^{\ast}(f)}{S_n(f)}\,df,
\end{align}
where $\hat{h}=h/\sqrt{\langle h, h \rangle}$ is the normalized GW strain,
$S_n(f)$ is the noise spectrum, $f_{\mathrm{max}}$ and $f_{\mathrm{min}}$ are
the relevant maximum and minimum frequencies for the integration. The mismatch
is a quantity that is closely related to the mean square error (MSE) between the
two waveforms, as it is often considered a weighted version of the MSE.

In the original calibration \citep{khan2016frequency,husa2016frequency},
training waveforms are hybrid waveforms of NR simulations and SpinAlignedEOB
(SEOB) waveforms. The low frequency inspiral part is taken from the SEOB
waveforms while the rest of the waveforms are taken from NR simulations.
Instead, we solely use NR waveforms for comparison, since most NR waveforms used
have long enough time series data, i.e.~$>15$ orbits \citep{boyle2019sxs}, in
which they are long enough to contain part of the inspiral segment and all
merger and ringdown frequency information. We take the frequency limits as
$f_{\mathrm{min}}=0.1f_{\mathrm{RD}}$ and $f_{\mathrm{max}}=1.2f_{\mathrm{RD}}$,
where $f_{\mathrm{RD}}$ is the frequency at ringdown. This range covers most of
the IMRPhenomD's frequency range, except the minimum frequency is set higher
than that in the original calibration due to NR length. When compared with
IMRPhenomC, the frequency range is slightly extended to have a higher maximum
frequency.

We choose to use two different noise spectra $S_n(f)$, namely the zero-detuned
high-power (\zdethp) noise spectrum and a constant spectrum. Since in any data
analysis tasks, model-generated waveforms will ultimately be used to compare
with GW observations, they are subjected to the sensitivity of detectors. Hence,
it is sensible to have waveforms calibrated with {\zdethp} spectrum rather than
a non-weighted spectrum. However, with sensitivity curve involved, we have to
choose a corresponding mass scale. Here, we simply choose $M=50M_{\odot}$ for
all waveforms, since this mass scale is common in LIGO observations. On the
other hand, we also recalibrated coefficients with the constant spectrum for a
more general purpose.

>>>>

In order to recalibrate the model, we need to define an objective function that
quantify the performance of the model. A common choice for such metric is the
\textit{mismatch} function \citep{husa2016frequency}. It is defined as
\begin{align} \label{eq:mismatch}
	\mathcal{M}(h_1, h_2)=1-\max_{t_0, \phi_0}\langle \hat{h}_1, \hat{h}_2\rangle,
\end{align}
where $h_{1,2}$ are the two GW waveform we are comparing, and $t_0$ and $\phi_0$
are time shift and phase shift respectively. The $\langle h_1, h_2 \rangle$ is
commonly referred as the inner product, which is defined as 
\begin{align}\label{eq:inner_prod}
	\langle h_1, h_2 \rangle = 4\Re\int_{f_{\mathrm{min}}}^{f_{\mathrm{max}}}\frac{h_1(f)h_2^{\ast}(f)}{S_n(f)}\,df,
\end{align}
where $\hat{h}=h/\sqrt{\langle h, h \rangle}$ is the normalized GW strain,
$S_n(f)$ is the power spectral density(PSD) of noise from the instrument, $f_{\mathrm{max}}$ and $f_{\mathrm{min}}$ are
the relevant maximum and minimum frequencies for the integration. The mismatch
is a quantity that is closely related to the mean square error (MSE) between the
two waveforms, as it is often considered a weighted version of the MSE.

\kw{Remind me why don't we use the hybrid waveforms again? Cause we couldn't do it?}
In the original calibration \citep{khan2016frequency,husa2016frequency},
training waveforms are hybrid waveforms of NR simulations and SpinAlignedEOB
(SEOB) waveforms. The low frequency inspiral part is taken from the SEOB
waveforms while the rest of the waveforms are taken from NR simulations.
Instead, we solely use NR waveforms for comparison, since most NR waveforms used
have long enough time series data, i.e.~$>15$ orbits \citep{boyle2019sxs}, in
which they are long enough to contain part of the inspiral segment and all
merger and ringdown frequency information. We take the frequency limits as
$f_{\mathrm{min}}=0.1f_{\mathrm{RD}}$ and $f_{\mathrm{max}}=1.2f_{\mathrm{RD}}$,
where $f_{\mathrm{RD}}$ is the frequency at ringdown. This range covers most of
the IMRPhenomD's frequency range, except the minimum frequency is set higher
than that in the original calibration due to NR length. When compared with
IMRPhenomC, the frequency range is slightly extended to have a higher maximum
frequency.

To compute the integral shown in Eq. \ref{eq:inner_prod}, one need to choose a
relevant noise PSD. Since a common goal for creating waveform approximent is to
deploy the waveform model in downstream data analysis tasks, a reasonable choice
for the noise PSD should be closely related to the instrument of interest. We
choose the zero-detuned high-power (\zdethp) noise PSD \kw{add citation} as our
first choice of noise PSD. Because the total mass of the system simple scales
the frequency of the waveform, we need to choose a corresponding mass scale to
match the frequency range of our noise PSD. Here, we choose $M=50M_{\odot}$ for
all waveforms, since this mass scale is common in LIGO observations. In addition
to a detector-dependent PSD, we are also interested in a more
instrument-agnostic case such that we can evaluate the effectiveness of the
recalibration without considering detector effect. In this case, we set the
noise PSD to be a constant value.
